### 2019-12-20 paper/conclusion.tex
After Andrei's comments in #7 and #8

The excess reactivity $\rho_e$ is calculated at zero burnup when all CRs are 
fully withdrawn. $\rho_e$ for $^{233}$U, reactor-grade Pu, and 
TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, 
respectively.

Five different absorbing materials are considered based on their neutronics and 
safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 is able to shut down the SD-TMSR initially loaded 
with transuranium vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

@@

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case), this makes the SSD clusters ineffective to shut down the reactor loaded 
with TRU.

@@

\section{Future work}
In Part II of this research effort we will evaluate effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using 
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors indent to investigate 
kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

>>>>

The excess reactivity $\rho_e$ is calculated at zero burnup when all CRs are 
fully withdrawn. The $\rho_e$ for $^{233}$U, reactor-grade Pu, and 
TRU are $1.65\pm0.04$ $\$$, $4.11\pm0.02$ $\$$, and $15.38\pm0.04$ $\$$, 
respectively.

Five different absorbing materials are considered based on their neutronics and 
safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with transuranium vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

@@

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case), this makes the SSD clusters unreliable to shut down the reactor loaded 
with TRU because the SSD clusters should provide a sufficient positive shutdown margin.

@@

Finally, the proposed design of CRs successfully control the excess reactivity and enhance the safety aspects of the SD-TMSR.

\section{Future work}
In Part II of this research effort we will evaluate effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using 
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

### 2019-12-20 paper/introduction.tex
After Andrei's comments in #7 and #8

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2019whole_core,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. MSR designs have a drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), the MSR is commonly load with larger amount of 
fuel than that required to achieve criticality (necessary for long term core 
operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is quite large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2019whole_core,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2019whole_core}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2019whole_core}. However, the most common and reliable procedure 
for reactor control is to insert or withdraw control rods made of material 
with large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of  
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

@@

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2019whole_core,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2019whole_core,ashraf2020Strategies,li_optimization_2018}. However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new 
fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation and shut down the reactor in case of  
emergency. Five different absorbing materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorbing materials, and shadowing 
effects at steady state calculation.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. MSR designs have a drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), the MSR is commonly load with larger amount of 
fuel than that required to achieve criticality (necessary for long term core 
operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is quite large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole}. However, the most common and reliable procedure 
for reactor control is to insert or withdraw control rods made of material 
with large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

@@

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}. However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new 
fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Five different absorbing materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorbing materials, and shadowing 
effects at steady state calculation.

### 2019-12-20 paper/methods.tex
After Andrei's comments in #7 and #8

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
\cite{li_optimization_2018,ashraf2019whole_core}. The core of the  
\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
and the outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the  
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2019whole_core}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the fuel 
tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The integral CRW is the total reactivity change due to the control rod full 
insertion or withdrawal. In contrast, the differential CRW is the amount of 
reactivity inserted per unit of withdrawal [$\$/cm$]. To calculate those 
parameters, we varied the position of CRs clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor 
after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
fraction of delayed neutrons at i$^{th}$ step. N is the number of steps.

>>>>

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
\cite{li_optimization_2018,ashraf2020whole}. The core of the 
\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
and the outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is 70LiF - 17.5BeF$_2$ - 
12.5(HM)F$_N$ mole\%, where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the fuel 
tubes that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the \gls{SD-TMSR} pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the \gls{SD-TMSR} are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The integral CRW is the total reactivity change due to the control rod full 
insertion or withdrawal. In contrast, the differential CRW is the amount of 
reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
parameters, we varied the position of CRs clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor 
after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
fraction of delayed neutrons at i$^{th}$ step. N is the number of steps.
